---
title: 'Pre-copulatory sexual selection predicts sexual size dimorphism: a meta-analysis of comparative studies'
author: "Lennart Winkler^1^, Robert P Freckleton^2^, Tamas Szekely^3^, ^4^ & Tim Janicke^1,5^ <br></br>  ^1^Applied Zoology, Technical University Dresden </br></br>^2^Department of Zoology, University of Oxford, South Parks Road, Oxford OX1 3PS, UK<br></br>^3^Milner Centre for Evolution, University of Bath, Bath, UK8</br></br>^4^Department of Evolutionary Zoology and Human Behaviour, University of Debrecen, Debrecen, Hungary</br></br> ^5^Centre d’Écologie Fonctionnelle et Évolutive, UMR 5175, CNRS, Université de Montpellier</br>"
subtitle: 'Main analyses'
site: workflowr::wflow_site
output:
  workflowr::wflow_html
---

Supplementary material reporting R code for the manuscript 'Pre-copulatory sexual selection predicts sexual size dimorphism: a meta-analysis of comparative studies'.
</br></br>
Additional analyses excluding studies that did not control for phylogenetic non-independence (Supplement 2) can be found at:
</br>
https://https://lennartwinkler.github.io/SSD_and_sexual_selection_2023/index2.html
</br>
# Load and prepare data
Before we started the analyses, we loaded all necessary packages and data.
```{r Load, message=FALSE, warning=FALSE, results='hide'}
rm(list = ls()) # Clear work environment

# Load R-packages ####
list_of_packages=cbind('ape','matrixcalc','metafor','Matrix','MASS','pwr','psych','multcomp','data.table','ggplot2','RColorBrewer','MCMCglmm','ggdist','cowplot','PupillometryR','dplyr','wesanderson','gridExtra')
lapply(list_of_packages, require, character.only = TRUE)

# Load data set ####
MetaData <- read.csv("./data/Data_SexSelSSD.csv", sep=";", header=TRUE) # Load data set

N_Studies <- length(summary(as.factor(MetaData$Study_ID))) # Number of included primary studies

Tree<- read.tree("./data/Pyologeny_SexSelSSD.txt") # Load phylogenetic tree

# Prune phylogenetic tree
MetaData_Class_Data <- unique(MetaData$Class)
Tree_Class<-drop.tip(Tree, Tree$tip.label[-na.omit(match(MetaData_Class_Data, Tree$tip.label))])
forcedC_Moderators <- as.matrix(forceSymmetric(vcv(Tree_Class, corr=TRUE)))

# Order moderator levels
MetaData$SexSel_Episode=as.factor(MetaData$SexSel_Episode)
MetaData$SexSel_Episode=relevel(MetaData$SexSel_Episode,c("post-copulatory"))
MetaData$SexSel_Episode=relevel(MetaData$SexSel_Episode,c("pre-copulatory"))
MetaData$Class=as.factor(MetaData$Class)
MetaData$z=as.numeric(MetaData$z)

# Set figure theme and colors
theme=theme(panel.border = element_blank(), 
            panel.background = element_blank(),
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(), 
            legend.position = c(0.2,0.5),
            legend.title = element_blank(),
            legend.text = element_text(colour="black", size=12),
            axis.line.x = element_line(colour = "black", linewidth = 1),
            axis.line.y = element_line(colour = "black", linewidth = 1),
            axis.text.x = element_text(face="plain", color="black", size=12, angle=0),
            axis.text.y = element_text(face="plain", color="black", size=12, angle=0),
            axis.title.x = element_text(size=14,face="plain", margin = margin(r=0,10,0,0)),
            axis.title.y = element_text(size=14,face="plain", margin = margin(r=10,0,0,0)),
            axis.ticks = element_line(linewidth = 1),
            axis.ticks.length = unit(.3, "cm"))

colpal=c('#003d6cff','#0c7accff','#5a9c97ff')

colpal2=brewer.pal(7, 'Dark2')
colpal3=brewer.pal(10, 'BrBG')
colpal4=c("grey50","grey65")
colpal5=c("#8C2D04","#CC4C02", "#EC7014", "#FE9929", "#FEC44F","#A8DDB5","#A8DDB5", "#7BCCC4", "#4EB3D3", "#2B8CBE", "#08589E")
colpal6=c("#8C2D04","#CC4C02", "#EC7014", "#FE9929", "#FEC44F","#A8DDB5", "#7BCCC4", "#4EB3D3", "#2B8CBE", "#08589E")
Meta_col=c('#5a9c97ff','#0c7accff','#003d6cff','black')
```

# Global models
We addressed the question if increasing sexual selection correlated with an increasingly male-biased SSD. For this we ran a global model including an observation-level index and the study identifier as random termson correlation coefficients that were positive if increasing sexual selection correlated with an increasingly male-biased SSD, but negative if increasing sexual selection correlated with an increasingly female-biased SSD. </br></br>
First, we ran a global model including the phylogeny:
```{r Global phylogenetic Model, warning=FALSE, message=FALSE}
Model_REML_Null         = rma.mv(r ~ 1, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_Null)
```

Second, we ran a global model without the phylogeny:
```{r Global non-phylogenetic Model, warning=FALSE, message=FALSE}
Model_cREML_Null         = rma.mv(r ~ 1, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_Null)
```

# Moderator tests for phylogenetic models
Next, we ran a series of models that test the effect of different moderators.</br>
Again we started with models including the phylogeny.

## Sexual selection episode
The first model explores the effect of the different episodes of sexual selection (i.e. pre-copulatory, post-copulatory or both):
```{r Sexual selection mode, warning=FALSE, message=FALSE}
MetaData$SexSel_Episode=relevel(MetaData$SexSel_Episode,c("pre-copulatory"))
Model_REML_by_SexSelEpisode = rma.mv(r ~ factor(SexSel_Episode), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SexSelEpisode)
```
We then re-leveled the model for post-hoc comparisons:
```{r Sexual selection mode (re-leveled), warning=FALSE, message=FALSE, results='hide'}
MetaData$SexSel_Episode=relevel(MetaData$SexSel_Episode,c("post-copulatory"))
Model_REML_by_SexSelEpisode2 = rma.mv(r ~ factor(SexSel_Episode), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SexSelEpisode2)

MetaData$SexSel_Episode=relevel(MetaData$SexSel_Episode,c("both"))
Model_REML_by_SexSelEpisode3 = rma.mv(r ~ factor(SexSel_Episode), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SexSelEpisode3)
```
Finally, we computed FDR corrected p-values:
```{r FDR corrected p-values for Sexual selection episode, warning=FALSE, message=FALSE}
tab1=as.data.frame(round(p.adjust(c(.0001, 0.3004, .0001), method = 'fdr'),digit=3),row.names=cbind("Pre-copulatory","Post-copulatory","Both"))
colnames(tab1)<-cbind('P-value')
tab1
```
## Plot sexual selection mode (Figure 3)

Here we plot the sexual selection mode moderator:
```{r Figure 3, warning=FALSE, message=FALSE, fig.align="left",fig.width = 7,fig.height=5, results='hide', fig.fullwidth=TRUE,fig.cap='Figure 3: Raincloud plot of correlation coefficients between SSD and the modes of sexual selection proxies (i.e. pre-copulatory, post-copulatory or both) including sample sizes and estimates with 95%CI from phylogenetic model.'}
MetaData$SexSel_Episode=factor(MetaData$SexSel_Episode, levels = c("both","post-copulatory" ,"pre-copulatory"))

ggplot(MetaData, aes(x=SexSel_Episode, y=r, fill = SexSel_Episode, colour = SexSel_Episode)) +
  geom_hline(yintercept=0, linetype="longdash", color = "black", linewidth=1)+
  geom_flat_violin(position = position_nudge(x = 0.25, y = 0),adjust =1, trim = F,alpha=0.6)+
  geom_point(position = position_jitter(width = .1), size = 2.5,alpha=0.6,stroke=0,shape=19)+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_REML_by_SexSelEpisode$ci.lb[1], x=3.25, xend= 3.25, yend= Model_REML_by_SexSelEpisode$ci.ub[1]), alpha=1,linewidth=1,color='black')+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_REML_by_SexSelEpisode2$ci.lb[1], x=2.25, xend= 2.25, yend= Model_REML_by_SexSelEpisode2$ci.ub[1]), alpha=1,linewidth=1,color='black')+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_REML_by_SexSelEpisode3$ci.lb[1], x=1.25, xend= 1.25, yend= Model_REML_by_SexSelEpisode3$ci.ub[1]), alpha=1,linewidth=1,color='black')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_REML_by_SexSelEpisode$b[1,1], x=3.25), size = 3.5,alpha=1,stroke=1,shape=21,fill='grey50',color='black')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_REML_by_SexSelEpisode2$b[1,1], x=2.25), size = 3.5,alpha=1,stroke=1,shape=21,fill='white',color='black')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_REML_by_SexSelEpisode3$b[1,1], x=1.25), size = 3.5,alpha=1,stroke=1,shape=21,fill='black',color='black')+
  ylab(expression(paste("Effect size (", italic("r"),')')))+xlab('Sexual selection episode')+coord_flip()+guides(fill = FALSE, colour = FALSE) +
  scale_color_manual(values =colpal)+
  scale_fill_manual(values =colpal)+
  scale_x_discrete(labels=c("Pre- and      \n post-copulatory","Post-copulatory" ,"Pre-copulatory"),expand=c(.1,0))+
  annotate("text", x=1, y=1.2, label= "n = 48",size=4.5) +
  annotate("text", x=2, y=1.2, label= "n = 19",size=4.5) +
  annotate("text", x=3, y=1.2, label= "n = 55",size=4.5) + theme
```

## Sexual selection category
Next we explored the effect of the sexual selection category (i.e. density, mating system, operational sex ratio (OSR), post-mating competition, pre-mating competition, trait-based, other):
```{r Sexual selection category, warning=FALSE, message=FALSE}
MetaData$SexSel_Category=as.factor(MetaData$SexSel_Category)
MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Postmating competition"))
Model_REML_by_SexSelCat = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SexSelCat)
```
We then re-leveled the model for post-hoc comparisons:
```{r Sexual selection category (re-leveled), warning=FALSE, message=FALSE, results='hide'}
MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Trait-based"))
Model_REML_by_SexSelCat2 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SexSelCat2)

MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Density"))
Model_REML_by_SexSelCat3 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SexSelCat3)

MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Premating competition"))
Model_REML_by_SexSelCat4 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SexSelCat4)

MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Mating system"))
Model_REML_by_SexSelCat5 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SexSelCat5)

MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("OSR"))
Model_REML_by_SexSelCat6 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SexSelCat6)

MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Other"))
Model_REML_by_SexSelCat7 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SexSelCat7)
```
Finally, we computed FDR corrected p-values:
```{r FDR corrected p-values for Sexual selection category, warning=FALSE, message=FALSE}
tab2=as.data.frame(round(p.adjust(c(0.1834, 0.8561, 0.0826, .0001, .0001, .0001, 0.0002), method = 'fdr'),digit=3),row.names=cbind("Postmating competition","Trait-based","Density",'Premating competition',"Mating system","OSR","Other"))
colnames(tab2)<-cbind('P-value')
tab2
```
## Plot sexual selection category (Figure S1)

Here we plot the sexual selection category moderator:
```{r Figure S1, warning=FALSE, message=FALSE, fig.align="left",fig.width = 8,fig.height=7, results='hide', fig.fullwidth=TRUE,fig.cap='Figure S1: Raincloud plot of correlation coefficients between SSD and different sexual selection categories including sample sizes and estimates with 95%CI from phylogenetic model.'}
MetaData$SexSel_Category=factor(MetaData$SexSel_Category, levels = rev(c( "Postmating competition","Trait-based" ,"Density","Premating competition" ,"Mating system" , "OSR", "Other")))

ggplot(MetaData, aes(x=SexSel_Category, y=r, fill = SexSel_Category, colour = SexSel_Category)) +
  geom_hline(yintercept=0, linetype="longdash", color = "black", linewidth=1)+
  geom_flat_violin(position = position_nudge(x = 0.25, y = 0),adjust =1, trim = F,alpha=0.6)+
  geom_point(position = position_jitter(width = .1), size = 2.5,alpha=0.6,stroke=0,shape=19)+
  geom_point(inherit.aes = F,mapping = aes(y=Model_REML_by_SexSelCat$b[1,1], x=7.25), size = 3.5,alpha=1,stroke=0,shape=19,color='grey30')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_REML_by_SexSelCat2$b[1,1], x=6.25), size = 3.5,alpha=1,stroke=0,shape=19,color='grey30')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_REML_by_SexSelCat3$b[1,1], x=5.25), size = 3.5,alpha=1,stroke=0,shape=19,color='grey30')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_REML_by_SexSelCat4$b[1,1], x=4.25), size = 3.5,alpha=1,stroke=0,shape=19,color='grey30')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_REML_by_SexSelCat5$b[1,1], x=3.25), size = 3.5,alpha=1,stroke=0,shape=19,color='grey30')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_REML_by_SexSelCat6$b[1,1], x=2.25), size = 3.5,alpha=1,stroke=0,shape=19,color='grey30')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_REML_by_SexSelCat7$b[1,1], x=1.25), size = 3.5,alpha=1,stroke=0,shape=19,color='grey30')+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_REML_by_SexSelCat$ci.lb[1], x=7.25, xend= 7.25, yend= Model_REML_by_SexSelCat$ci.ub[1]), alpha=1,linewidth=1,color='grey30')+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_REML_by_SexSelCat2$ci.lb[1], x=6.25, xend= 6.25, yend= Model_REML_by_SexSelCat2$ci.ub[1]), alpha=1,linewidth=1,color='grey30')+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_REML_by_SexSelCat3$ci.lb[1], x=5.25, xend= 5.25, yend= Model_REML_by_SexSelCat3$ci.ub[1]), alpha=1,linewidth=1,color='grey30')+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_REML_by_SexSelCat4$ci.lb[1], x=4.25, xend= 4.25, yend= Model_REML_by_SexSelCat4$ci.ub[1]), alpha=1,linewidth=1,color='grey30')+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_REML_by_SexSelCat5$ci.lb[1], x=3.25, xend= 3.25, yend= Model_REML_by_SexSelCat5$ci.ub[1]), alpha=1,linewidth=1,color='grey30')+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_REML_by_SexSelCat6$ci.lb[1], x=2.25, xend= 2.25, yend= Model_REML_by_SexSelCat6$ci.ub[1]), alpha=1,linewidth=1,color='grey30')+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_REML_by_SexSelCat7$ci.lb[1], x=1.25, xend= 1.25, yend= Model_REML_by_SexSelCat7$ci.ub[1]), alpha=1,linewidth=1,color='grey30')+
  ylab(expression(paste("Effect size (", italic("r"),')')))+xlab('Sexual selection category')+coord_flip()+guides(fill = FALSE, colour = FALSE) +
  scale_color_manual(values =colpal2)+
  scale_fill_manual(values =colpal2)+
  scale_x_discrete(labels=rev(c( "Post-mating\ncompetition","Trait-based" ,"Population\ndensity","Pre-mating\ncompetition" ,"Mating\nsystem" , "Sex ratio", "Other")),expand=c(.1,0))+
  annotate("text", x=7, y=1.2, label= "n = 19",size=4.5) +
  annotate("text", x=6, y=1.2, label= "n = 17",size=4.5) +
  annotate("text", x=5, y=1.2, label= "n = 5",size=4.5) +
  annotate("text", x=4, y=1.2, label= "n = 22",size=4.5) +
  annotate("text", x=3, y=1.2, label= "n = 36",size=4.5) +
  annotate("text", x=2, y=1.2, label= "n = 6",size=4.5) +
  annotate("text", x=1, y=1.2, label= "n = 17",size=4.5) + theme
```

## Type of SSD measure
Next we explored the effect of the type of SSD measure (i.e. body mass or size):
```{r Type of SSD measure, warning=FALSE, message=FALSE}
MetaData$SSD_Proxy=as.factor(MetaData$SSD_Proxy)
MetaData$SSD_Proxy=relevel(MetaData$SSD_Proxy,c("Body mass"))
Model_REML_by_SSDMeasure = rma.mv(r ~ SSD_Proxy, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SSDMeasure)
```
We then re-leveled the model for post-hoc comparisons:
```{r Type of SSD measure (re-leveled), warning=FALSE, message=FALSE, results='hide'}
MetaData$SSD_Proxy=relevel(MetaData$SSD_Proxy,c("Body size"))
Model_REML_by_SSDMeasure2 = rma.mv(r ~ SSD_Proxy, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SSDMeasure2)
```
Finally, we computed FDR corrected p-values:
```{r FDR corrected p-values for Type of SSD measure, warning=FALSE, message=FALSE}
tab3=as.data.frame(round(p.adjust(c(.0001, .0001), method = 'fdr'),digit=3),row.names=cbind("Body mass","Body size"))
colnames(tab3)<-cbind('P-value')
tab3
```

## Plot Type of SSD measure (Figure S2A)

Here we plot the type of SSD measure moderator:
```{r Figure S2A, warning=FALSE, message=FALSE, fig.align="left",fig.width = 8,fig.height=7, results='hide', fig.fullwidth=TRUE,fig.cap='Figure S2A: Raincloud plot of correlation coefficients for different types of SSD measures (i.e. body mass or size) including sample sizes and estimates with 95% CI from phylogenetic model.'}
MetaData_NAProxy=MetaData[!is.na(MetaData$SSD_Proxy),]
MetaData_NAProxy$SSD_Proxy=as.factor(MetaData_NAProxy$SSD_Proxy)
MetaData_NAProxy$SSD_Proxy=relevel(MetaData_NAProxy$SSD_Proxy,c("Body size"))

ggplot(MetaData_NAProxy, aes(x=SSD_Proxy, y=r, fill = SSD_Proxy, colour = SSD_Proxy)) +
  geom_hline(yintercept=0, linetype="longdash", color = "black", linewidth=1)+
  geom_flat_violin(position = position_nudge(x = 0.25, y = 0),adjust =1, trim = F,alpha=0.6)+
  geom_point(position = position_jitter(width = .1), size = 2.5,alpha=0.6,stroke=0,shape=19)+
  geom_point(inherit.aes = F,mapping = aes(y=Model_REML_by_SSDMeasure$b[1,1], x=2.25), size = 3.5,alpha=1,stroke=0,shape=19,color='grey30')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_REML_by_SSDMeasure2$b[1,1], x=1.25), size = 3.5,alpha=1,stroke=0,shape=19,color='grey30')+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_REML_by_SSDMeasure$ci.lb[1], x=2.25, xend= 2.25, yend= Model_REML_by_SSDMeasure$ci.ub[1]), alpha=1,linewidth=1,color='grey30')+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_REML_by_SSDMeasure2$ci.lb[1], x=1.25, xend= 1.25, yend= Model_REML_by_SSDMeasure2$ci.ub[1]), alpha=1,linewidth=1,color='grey30')+
  ylab(expression(paste("Effect size (", italic("r"),')')))+xlab('SSD proxy')+coord_flip()+guides(fill = FALSE, colour = FALSE) +
  scale_color_manual(values =colpal4)+
  scale_fill_manual(values =colpal4)+
  scale_x_discrete(labels=rev(c("Body \nmass ","Body \n size ")),expand=c(.15,0))+
  annotate("text", x=2, y=1.1, label= "n = 57",size=3.5) +
  annotate("text", x=1, y=1.1, label= "n = 63",size=3.5)  + theme
```

## SSD measure controlled for body size?
Next we explored the effect if the primary study controlled the SSD for body size (i.e. uncontrolled or controlled):
```{r SSD measure controlled, warning=FALSE, message=FALSE}
MetaData$BodySizeControlled=as.factor(MetaData$BodySizeControlled)
MetaData$BodySizeControlled=relevel(MetaData$BodySizeControlled,c("No"))
Model_REML_by_BodySizeCont = rma.mv(r ~ BodySizeControlled, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_BodySizeCont)
```
We then re-leveled the model for post-hoc comparisons:
```{r SSD measure controlled (re-leveled), warning=FALSE, message=FALSE, results='hide'}
MetaData$BodySizeControlled=relevel(MetaData$BodySizeControlled,c("Yes"))
Model_REML_by_BodySizeCont2 = rma.mv(r ~ BodySizeControlled, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_BodySizeCont2)
```
Finally, we computed FDR corrected p-values:
```{r FDR corrected p-values for SSD measure controlled, warning=FALSE, message=FALSE}
tab4=as.data.frame(round(p.adjust(c(.0001, 0.0517), method = 'fdr'),digit=3),row.names=cbind("uncontrolled","controlled"))
colnames(tab4)<-cbind('P-value')
tab4
```
## Plot: SSD measure controlled for body size? (Figure S2B)

Here we plot effect sizes if type of SSD measure controlled for body size:
```{r Figure S2B, warning=FALSE, message=FALSE, fig.align="left",fig.width = 8,fig.height=7, results='hide', fig.fullwidth=TRUE,fig.cap='Figure S2B: Raincloud plot of correlation coefficients for primary studies controlling SSD for body size or mass (uncontrolled or controlled) including sample sizes and estimates with 95% CI from phylogenetic model.'}
MetaData$BodySizeControlled=as.factor(MetaData$BodySizeControlled)
MetaData$BodySizeControlled=relevel(MetaData$BodySizeControlled,c("Yes"))

ggplot(MetaData, aes(x=BodySizeControlled, y=r, fill = BodySizeControlled, colour = BodySizeControlled)) +
  geom_hline(yintercept=0, linetype="longdash", color = "black", linewidth=1)+
  geom_flat_violin(position = position_nudge(x = 0.25, y = 0),adjust =1, trim = F,alpha=0.6)+
  geom_point(position = position_jitter(width = .1), size = 2.5,alpha=0.6,stroke=0,shape=19)+
  geom_point(inherit.aes = F,mapping = aes(y=Model_REML_by_BodySizeCont$b[1,1], x=2.25), size = 3.5,alpha=1,stroke=0,shape=19,color='grey30')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_REML_by_BodySizeCont2$b[1,1], x=1.25), size = 3.5,alpha=1,stroke=0,shape=19,color='grey30')+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_REML_by_BodySizeCont$ci.lb[1], x=2.25, xend= 2.25, yend= Model_REML_by_BodySizeCont$ci.ub[1]), alpha=1,linewidth=1,color='grey30')+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_REML_by_BodySizeCont2$ci.lb[1], x=1.25, xend= 1.25, yend= Model_REML_by_BodySizeCont2$ci.ub[1]), alpha=1,linewidth=1,color='grey30')+
  ylab(expression(paste("Effect size (", italic("r"),')')))+xlab('Controlling SSD \n for body size or mass')+coord_flip()+guides(fill = FALSE, colour = FALSE) +
  scale_color_manual(values =colpal4)+
  scale_fill_manual(values =colpal4)+
  scale_x_discrete(labels=(c("Controlled","Uncontrolled")),expand=c(.15,0))+
  annotate("text", x=2, y=1.1, label= "n = 105",size=3.5) +
  annotate("text", x=1, y=1.1, label= "n = 17",size=3.5)  + theme
```

## Phylogentic vs non-phylogenetic studies
Next we explored the effect of studies controlling for phylogeny vs non-phylogenetic studies:
```{r Type of Phylogentic vs non-phylogenetic studies, warning=FALSE, message=FALSE}
MetaData$PhyloControlled=as.factor(MetaData$PhyloControlled)
MetaData$PhyloControlled=relevel(MetaData$PhyloControlled,c("No"))
Model_cREML_by_Phylo = rma.mv(r ~ PhyloControlled, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_cREML_by_Phylo)
```
We then re-leveled the model for post-hoc comparisons:
```{r Type of Phylogentic vs non-phylogenetic studies (re-leveled), warning=FALSE, message=FALSE, results='hide'}
MetaData$PhyloControlled=relevel(MetaData$PhyloControlled,c("Yes"))
Model_cREML_by_Phylo2 = rma.mv(r ~ PhyloControlled, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_cREML_by_Phylo2)
```
Finally, we computed FDR corrected p-values:
```{r FDR corrected p-values for Phylogentic vs non-phylogenetic studies, warning=FALSE, message=FALSE}
tab5=as.data.frame(round(p.adjust(c(0.0001, 0.0027), method = 'fdr'),digit=3),row.names=cbind("Non-phylogenetic","With phylogeny"))
colnames(tab5)<-cbind('P-value')
tab5
```

## Plot Phylogentic vs non-phylogenetic studies (Figure S2C)

Here we plot the type of SSD measure moderator:
```{r Figure S2C, warning=FALSE, message=FALSE, fig.align="left",fig.width = 8,fig.height=7, results='hide', fig.fullwidth=TRUE,fig.cap='Figure S2C: Raincloud plot of correlation coefficients for non-phylogenetic and phylogenetic analyses in primary studies including sample sizes and estimates with 95% CI from phylogenetic model (Table 4).'}
MetaData$PhyloControlled=as.factor(MetaData$PhyloControlled)
MetaData$PhyloControlled=relevel(MetaData$PhyloControlled,c("No"))

ggplot(MetaData, aes(x=PhyloControlled, y=r, fill = PhyloControlled, colour = PhyloControlled)) +
  geom_hline(yintercept=0, linetype="longdash", color = "black", linewidth=1)+
  geom_flat_violin(position = position_nudge(x = 0.25, y = 0),adjust =1, trim = F,alpha=0.6)+
  geom_point(position = position_jitter(width = .1), size = 2.5,alpha=0.6,stroke=0,shape=19)+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Phylo2$b[1,1], x=2.25), size = 3.5,alpha=1,stroke=0,shape=19,color='grey30')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Phylo$b[1,1], x=1.25), size = 3.5,alpha=1,stroke=0,shape=19,color='grey30')+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_cREML_by_Phylo2$ci.lb[1], x=2.25, xend= 2.25, yend= Model_cREML_by_Phylo2$ci.ub[1]), alpha=1,linewidth=1,color='grey30')+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_cREML_by_Phylo$ci.lb[1], x=1.25, xend= 1.25, yend= Model_cREML_by_Phylo$ci.ub[1]), alpha=1,linewidth=1,color='grey30')+
  ylab(expression(paste("Effect size (", italic("r"),')')))+xlab('Controlling for phylogeny')+coord_flip()+guides(fill = FALSE, colour = FALSE) +
  scale_color_manual(values =colpal4)+
  scale_fill_manual(values =colpal4)+
  scale_x_discrete(labels=(c("Phylogenetically \n uncorrected ","Phylogenetically \n corrected ")),expand=c(.15,0))+
  annotate("text", x=1, y=1.1, label= "n = 20",size=3.5) +
  annotate("text", x=2, y=1.1, label= "n = 102",size=3.5)  + theme
```
## Percentage of species with female-biased SSD
There was variation in the primary studies regarding the typical SSD in the studied taxa (i.e. some studies focused on taxa with more male-biased SSD, while others on taxa with more female-biased SSD). Still, there was no significant relationship between the percentage of species with a female-biased SSD and effect sizes.

```{r Percentage of species with female-biased SSD, warning=FALSE, message=FALSE}
MetaData_SSDbias=MetaData
MetaData_SSDbias=MetaData_SSDbias[!is.na(MetaData_SSDbias$SSD_SexBias_in_perc_F),]
Model_REML_SSbias         = rma.mv(r ~ SSD_SexBias_in_perc_F, V=Var_r, data = MetaData_SSDbias, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_SSbias)
```

## Figure S3A
```{r Figure S3A, warning=FALSE, message=FALSE, fig.align="left",fig.width = 7,fig.height=5, results='hide', fig.fullwidth=TRUE,fig.cap='Figure S3A: Scatter plot of the sPercentage of species with a female-biased SSD. Dashed line marks a correlation coefficient of zero, black line represents predictions from REML model (controlling for phylogeny) and grey area represents 95% CI on model predictions.'}

model_p1 <- predict(Model_REML_SSbias) # Extract model predictions

ggplot(MetaData_SSDbias, aes(x=as.numeric(SSD_SexBias_in_perc_F), y=r)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  theme(axis.text=element_text(size=13),
        axis.title=element_text(size=14))+ theme(legend.position="none")+
  geom_point(shape=16, size = 3,alpha=0.5)+xlab('% of species with \n female-biased SSD')+ylab(expression(paste("Effect size (", italic("r"),')')))+
  geom_hline(yintercept=0, linetype="dashed", color = "black", linewidth=1)+
  geom_line( aes(y = model_p1$pred), size = 1)+ 
  geom_ribbon( aes(ymin = model_p1$ci.lb, ymax = model_p1$ci.ub, color = 'black',linetype=NA), alpha = .15,show.legend = F, outline.type = "both") +
  theme
```

## Test for publication bias
To test for publication bias, we transformed r into z scores and ran multilevel mixed-effects models (restricted maximum likelihood) with z as the predictor and its standard error as the response with study ID and an observation level random effect. Models were weight by the mean standard error of z across all studies. While the variance in r depends on the effect size and the sample size, the variance in z is only dependent on the sample size. Hence, if z values correlate with the variance in z, this indicates that small studies were only published, if the effect was large, suggesting publication bias.

```{r Test for publication bias, warning=FALSE, message=FALSE}
Model_REML_PublBias         = rma.mv(z ~ SE_z, V=rep((mean(SE_z)*mean(SE_z))*N,length(SE_z)), data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML",control=list(rel.tol=1e-8))
summary(Model_REML_PublBias)
```

## Figure S3B
```{r Figure S3B, warning=FALSE, message=FALSE, fig.align="left",fig.width = 7,fig.height=5, results='hide', fig.fullwidth=TRUE,fig.cap='Figure S3B: Scatter plot of the standard error in z scores of each study against the z score of each primary study (transformed correlation coefficients). Dashed line marks a correlation coefficient of zero, black line represents predictions from REML model (controlling for phylogeny) and grey area represents 95% CI on model predictions.'}
# Extract model predictions
model_p2 <- predict(Model_REML_PublBias)

ggplot(MetaData, aes(x=SE_z, y=z)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  theme(axis.text=element_text(size=13),
        axis.title=element_text(size=14))+ theme(legend.position="none")+ylab(expression(paste("Effect size (", italic("z"),')')))+
  geom_point(shape=16, size = 3,alpha=0.5)+xlab('Standard error')+
  geom_hline(yintercept=0, linetype="dashed", color = "black", linewidth=1)+
  geom_line( aes(y = model_p2$pred), size = 1)+ 
  geom_ribbon( aes(ymin = model_p2$ci.lb, ymax = model_p2$ci.ub, color = 'black',linetype=NA), alpha = .15,show.legend = F, outline.type = "both") +
  theme
```

## Publication year
Next we explored the effect of the publication year of each study:
```{r Publication year, warning=FALSE, message=FALSE}
Model_REML_by_Year = rma.mv(r ~ Year, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_Year)
```

## Plot publication year (Figure S3C)

Here we plot the publication year:
```{r Figure S3C, warning=FALSE, message=FALSE, fig.align="left",fig.width = 7,fig.height=5, results='hide', fig.fullwidth=TRUE,fig.cap='Figure S3C: Scatter plot of correlation coefficients against the publication year of each study. Dashed line marks a correlation coefficient of zero, black line represents predictions from REML model (controlling for phylogeny) and grey area represents 95% CI on model predictions.'}
# Extract model predictions
Model_REML_by_Year = rma.mv(r ~ Year, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
model_p4 <- predict(Model_REML_by_Year)

ggplot(MetaData, aes(x=as.numeric(Year), y=r)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  theme(axis.text=element_text(size=13),
        axis.title=element_text(size=14))+ theme(legend.position="none")+
  geom_point(shape=16, size = 3,alpha=0.5)+xlab('Publication year')+ylab(expression(paste("Effect size (", italic("r"),')')))+
  geom_hline(yintercept=0, linetype="dashed", color = "black", linewidth=1)+
  geom_line( aes(y = model_p4$pred), size = 1)+ 
  geom_ribbon( aes(ymin = model_p4$ci.lb, ymax = model_p4$ci.ub, color = 'black',linetype=NA), alpha = .15,show.legend = F, outline.type = "both") +
  theme
```

# Moderator tests for non-phylogenetic models
Here we ran all models without the phylogeny.

## Sexual selection episode
The first model explores the effect of the sexual selection episode (i.e. pre-copulatory, post-copulatory or both):
```{r Sexual selection episode non-phylogenetic models, warning=FALSE, message=FALSE}
MetaData$SexSel_Episode=relevel(MetaData$SexSel_Episode,c("pre-copulatory"))
Model_REML_by_cSexSelEpisode = rma.mv(r ~ factor(SexSel_Episode), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cSexSelEpisode)
```
We then re-leveled the model for post-hoc comparisons:
```{r Sexual selection episode (re-leveled) non-phylogenetic models, warning=FALSE, message=FALSE, results='hide'}
MetaData$SexSel_Episode=relevel(MetaData$SexSel_Episode,c("post-copulatory"))
Model_REML_by_cSexSelEpisode2 = rma.mv(r ~ factor(SexSel_Episode), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cSexSelEpisode2)

MetaData$SexSel_Episode=relevel(MetaData$SexSel_Episode,c("both"))
Model_REML_by_cSexSelEpisode3 = rma.mv(r ~ factor(SexSel_Episode), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index),  method = "REML")
summary(Model_REML_by_cSexSelEpisode3)
```
Finally, we computed FDR corrected p-values:
```{r FDR corrected p-values for Sexual selection Episode non-phylogenetic models, warning=FALSE, message=FALSE}
tab1=as.data.frame(round(p.adjust(c(0.0001, 0.2970, .0001), method = 'fdr'),digit=3),row.names=cbind("Pre-copulatory","Post-copulatory","Both"))
colnames(tab1)<-cbind('P-value')
tab1
```

## Sexual selection category
Next we explored the effect of the sexual selection category (i.e. density, mating system, operational sex ratio (OSR), post-mating competition, pre-mating competition, trait-based, other):
```{r Sexual selection category non-phylogenetic models, warning=FALSE, message=FALSE}
MetaData$SexSel_Category=as.factor(MetaData$SexSel_Category)
MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Postmating competition"))
Model_REML_by_cSexSelCat = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cSexSelCat)
```
We then re-leveled the model for post-hoc comparisons:
```{r Sexual selection category (re-leveled) non-phylogenetic models, warning=FALSE, message=FALSE, results='hide'}
MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Trait-based"))
Model_REML_by_cSexSelCat2 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cSexSelCat2)

MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Density"))
Model_REML_by_cSexSelCat3 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cSexSelCat3)

MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Premating competition"))
Model_REML_by_cSexSelCat4 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cSexSelCat4)

MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Mating system"))
Model_REML_by_cSexSelCat5 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cSexSelCat5)

MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("OSR"))
Model_REML_by_cSexSelCat6 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cSexSelCat6)

MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Other"))
Model_REML_by_cSexSelCat7 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cSexSelCat7)
```
Finally, we computed FDR corrected p-values:
```{r FDR corrected p-values for Sexual selection category non-phylogenetic models, warning=FALSE, message=FALSE}
tab2=as.data.frame(round(p.adjust(c(0.2930, 0.9215, 0.0124, .0001, .0001, .0001, .0001), method = 'fdr'),digit=3),row.names=cbind("Postmating competition","Trait-based","Density",'Premating competition',"Mating system","OSR","Other"))
colnames(tab2)<-cbind('P-value')
tab2
```

## Phylogenetic classes
Next we explored the effect of the phylogenetic classes:
```{r Phylogenetic classes, warning=FALSE, message=FALSE}
MetaData$Class=relevel(MetaData$Class,c("Actinopterygii"))
Model_cREML_by_Class5 = rma.mv(r ~ Class, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Class5)

MetaData$Class=relevel(MetaData$Class,c("Amphibia"))
Model_cREML_by_Class4 = rma.mv(r ~ Class, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Class4)

MetaData$Class=relevel(MetaData$Class,c("Animalia"))
Model_cREML_by_Class11 = rma.mv(r ~ Class, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Class11)

MetaData$Class=relevel(MetaData$Class,c("Aves"))
Model_cREML_by_Class = rma.mv(r ~ Class, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Class)

MetaData$Class=relevel(MetaData$Class,c("Insecta"))
Model_cREML_by_Class8 = rma.mv(r ~ Class, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Class8)

MetaData$Class=relevel(MetaData$Class,c("Malacostraca"))
Model_cREML_by_Class7 = rma.mv(r ~ Class, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Class7)

MetaData$Class=relevel(MetaData$Class,c("Mammalia"))
Model_cREML_by_Class3 = rma.mv(r ~ Class, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Class3)

MetaData$Class=relevel(MetaData$Class,c("Nematoda"))
Model_cREML_by_Class10 = rma.mv(r ~ Class, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Class10)

MetaData$Class=relevel(MetaData$Class,c("Pisces"))
Model_cREML_by_Class6 = rma.mv(r ~ Class, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Class6)

MetaData$Class=relevel(MetaData$Class,c("Reptilia"))
Model_cREML_by_Class2 = rma.mv(r ~ Class, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Class2)

MetaData$Class=relevel(MetaData$Class,c("Trematoda"))
Model_cREML_by_Class9 = rma.mv(r ~ Class, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Class9)
```
Finally, we computed FDR corrected p-values:
```{r FDR corrected p-values for Phylogenetic classes, warning=FALSE, message=FALSE}
tab2=as.data.frame(round(p.adjust(c(.0001, 0.1806, .0001, 0.4415, 0.0454, 0.3352, 0.9948, 0.0009, 0.7710, 0.0796, 0.3071), method = 'fdr'),digit=3),row.names=cbind( "Animalia","Nematoda","Trematoda","Insecta","Malacostraca","Pisces" ,"Actinopterygii","Amphibia","Mammalia","Reptilia","Aves"))
colnames(tab2)<-cbind('P-value')
tab2
```

## Plot phylogenetic classes (Figure 1)

Here we plot the phylogenetic classes:
```{r Figure 1, warning=FALSE, message=FALSE, fig.align="left",fig.width = 7,fig.height=5, results='hide', fig.fullwidth=TRUE,fig.cap='Figure 1: Phylogeny based on classes including sample sizes for the number of studies and number of effect sizes, respectively, and estimates with 95%CI from non-phylogenetic model.'}
MetaData$Class=as.factor(MetaData$Class)
MetaData$Class=factor(MetaData$Class, levels = (c("Animalia","Nematoda","Trematoda","Insecta","Malacostraca","Pisces" ,"Actinopterygii","Amphibia","Mammalia","Reptilia","Aves")))
MetaData_sorted=MetaData
MetaData_sorted$Class[MetaData_sorted$Class=='Pisces']='Actinopterygii'

ggplot() +
  geom_hline(yintercept=0, linetype="longdash", color = "black", linewidth=1)+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class$ci.lb[1], x=11.35, xend= 11.35, yend= Model_cREML_by_Class$ci.ub[1]),linewidth=1,color=colpal5[11], alpha=1)+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class2$ci.lb[1], x=10.35, xend= 10.35, yend= Model_cREML_by_Class2$ci.ub[1]), alpha=1,linewidth=1,color=colpal5[10])+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class3$ci.lb[1], x=9.35, xend= 9.35, yend= Model_cREML_by_Class3$ci.ub[1]), alpha=1,linewidth=1,color=colpal5[9])+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class4$ci.lb[1], x=8.35, xend= 8.35, yend= Model_cREML_by_Class4$ci.ub[1]), alpha=1,linewidth=1,color=colpal5[8])+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class5$ci.lb[1], x=7.35, xend= 7.35, yend= Model_cREML_by_Class5$ci.ub[1]), alpha=1,linewidth=1,color=colpal5[7])+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class6$ci.lb[1], x=6.35, xend= 6.35, yend= Model_cREML_by_Class6$ci.ub[1]), alpha=1,linewidth=1,color=colpal5[6])+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class7$ci.lb[1], x=5.35, xend= 5.35, yend= Model_cREML_by_Class7$ci.ub[1]), alpha=1,linewidth=1,color=colpal5[5])+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class8$ci.lb[1], x=4.35, xend= 4.35, yend= Model_cREML_by_Class8$ci.ub[1]), alpha=1,linewidth=1,color=colpal5[4])+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class9$ci.lb[1], x=3.35, xend= 3.35, yend= Model_cREML_by_Class9$ci.ub[1]), alpha=1,linewidth=1,color=colpal5[3])+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class10$ci.lb[1], x=2.35, xend= 2.35, yend= Model_cREML_by_Class10$ci.ub[1]), alpha=1,linewidth=1,color=colpal5[2])+
  geom_segment(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class11$ci.lb[1], x=1.35, xend= 1.35, yend= Model_cREML_by_Class11$ci.ub[1]), alpha=1,linewidth=1,color=colpal5[1])+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class$b[1,1], x=11.35), size = 3.5,alpha=1,stroke=0,shape=19,color='white')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class2$b[1,1], x=10.35), size = 3.5,alpha=1,stroke=0,shape=19,color='white')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class3$b[1,1], x=9.35), size = 3.5,alpha=1,stroke=0,shape=19,color='white')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class4$b[1,1], x=8.35), size = 3.5,alpha=1,stroke=0,shape=19,color='white')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class5$b[1,1], x=7.35), size = 3.5,alpha=1,stroke=0,shape=19,color='white')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class6$b[1,1], x=6.35), size = 3.5,alpha=1,stroke=0,shape=19,color='white')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class7$b[1,1], x=5.35), size = 3.5,alpha=1,stroke=0,shape=19,color='white')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class8$b[1,1], x=4.35), size = 3.5,alpha=1,stroke=0,shape=19,color='white')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class9$b[1,1], x=3.35), size = 3.5,alpha=1,stroke=0,shape=19,color='white')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class10$b[1,1], x=2.35), size = 3.5,alpha=1,stroke=0,shape=19,color='white')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class11$b[1,1], x=1.35), size = 3.5,alpha=1,stroke=0,shape=19,color='white')+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class$b[1,1], x=11.35), size = 3.5,alpha=1,stroke=0,shape=19,color=colpal5[11])+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class2$b[1,1], x=10.35), size = 3.5,alpha=1,stroke=0,shape=19,color=colpal5[10])+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class3$b[1,1], x=9.35), size = 3.5,alpha=1,stroke=0,shape=19,color=colpal5[9])+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class4$b[1,1], x=8.35), size = 3.5,alpha=1,stroke=0,shape=19,color=colpal5[8])+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class5$b[1,1], x=7.35), size = 3.5,alpha=1,stroke=0,shape=19,color=colpal5[7])+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class6$b[1,1], x=6.35), size = 3.5,alpha=1,stroke=0,shape=19,color=colpal5[6])+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class7$b[1,1], x=5.35), size = 3.5,alpha=1,stroke=0,shape=19,color=colpal5[5])+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class8$b[1,1], x=4.35), size = 3.5,alpha=1,stroke=0,shape=19,color=colpal5[4])+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class9$b[1,1], x=3.35), size = 3.5,alpha=1,stroke=0,shape=19,color=colpal5[3])+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class10$b[1,1], x=2.35), size = 3.5,alpha=1,stroke=0,shape=19,color=colpal5[2])+
  geom_point(inherit.aes = F,mapping = aes(y=Model_cREML_by_Class11$b[1,1], x=1.35), size = 3.5,alpha=1,stroke=0,shape=19,color=colpal5[1])+
  ylab(expression(paste("Effect size (", italic("r"),')')))+xlab('Class')+coord_flip()+guides(fill = FALSE, colour = FALSE) +
  scale_x_discrete(labels=(c("Animalia","Nematoda","Trematoda","Insecta","Malacostraca","Pisces" ,"Actinopterygii","Amphibia","Mammalia","Reptilia","Aves")),expand=c(.1,0))+
  geom_point(data=MetaData,aes(x=Class, y=r, fill = Class, colour = Class),position = position_jitter(width = .1), size = 2.5,alpha=0.6,stroke=0,shape=19)+
  scale_color_manual(values =colpal5)+
  scale_fill_manual(values =colpal5)+
  theme
```

## Type of SSD measure
Next we explored the effect of the type of SSD measure (i.e. body mass or size):
```{r Type of SSD measure non-phylogenetic models, warning=FALSE, message=FALSE}
MetaData$SSD_Proxy=as.factor(MetaData$SSD_Proxy)
MetaData$SSD_Proxy=relevel(MetaData$SSD_Proxy,c("Body mass"))
Model_REML_by_cSSDMeasure = rma.mv(r ~ SSD_Proxy, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cSSDMeasure)
```
We then re-leveled the model for post-hoc comparisons:
```{r Type of SSD measure (re-leveled) non-phylogenetic models, warning=FALSE, message=FALSE, results='hide'}
MetaData$SSD_Proxy=relevel(MetaData$SSD_Proxy,c("Body size"))
Model_REML_by_cSSDMeasure2 = rma.mv(r ~ SSD_Proxy, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cSSDMeasure2)
```
Finally, we computed FDR corrected p-values:
```{r FDR corrected p-values for Type of SSD measure non-phylogenetic models, warning=FALSE, message=FALSE}
tab3=as.data.frame(round(p.adjust(c(.0001, .0001), method = 'fdr'),digit=3),row.names=cbind("Body mass","Body size"))
colnames(tab3)<-cbind('P-value')
tab3
```

## SSD measure controlled for body size?
Next we explored the effect if the primary study controlled the SSD for body size (i.e. uncontrolled or controlled):
```{r SSD measure controlled non-phylogenetic models, warning=FALSE, message=FALSE}
MetaData$BodySizeControlled=as.factor(MetaData$BodySizeControlled)
MetaData$BodySizeControlled=relevel(MetaData$BodySizeControlled,c("No"))
Model_REML_by_cBodySizeCont = rma.mv(r ~ BodySizeControlled, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cBodySizeCont)
```
We then re-leveled the model for post-hoc comparisons:
```{r SSD measure controlled (re-leveled) non-phylogenetic models, warning=FALSE, message=FALSE, results='hide'}
MetaData$BodySizeControlled=relevel(MetaData$BodySizeControlled,c("Yes"))
Model_REML_by_cBodySizeCont2 = rma.mv(r ~ BodySizeControlled, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cBodySizeCont2)
```
Finally, we computed FDR corrected p-values:
```{r FDR corrected p-values for SSD measure controlled non-phylogenetic models, warning=FALSE, message=FALSE}
tab4=as.data.frame(round(p.adjust(c(.0001, 0.0172), method = 'fdr'),digit=3),row.names=cbind("uncontrolled","controlled"))
colnames(tab4)<-cbind('P-value')
tab4
```

## Phylogentic vs non-phylogenetic studies
Next we explored the effect of studies controlling for phylogeny vs non-phylogenetic studies:
```{r Type of Phylogentic vs non-phylogenetic studies non-phylogenetic models, warning=FALSE, message=FALSE}
MetaData$PhyloControlled=as.factor(MetaData$PhyloControlled)
MetaData$PhyloControlled=relevel(MetaData$PhyloControlled,c("No"))
Model_cREML_by_cPhylo = rma.mv(r ~ PhyloControlled, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_cPhylo)
```
We then re-leveled the model for post-hoc comparisons:
```{r Type of Phylogentic vs non-phylogenetic studies (re-leveled) non-phylogenetic models, warning=FALSE, message=FALSE, results='hide'}
MetaData$PhyloControlled=relevel(MetaData$PhyloControlled,c("Yes"))
Model_cREML_by_cPhylo2 = rma.mv(r ~ PhyloControlled, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_cPhylo2)
```
Finally, we computed FDR corrected p-values:
```{r FDR corrected p-values for Phylogentic vs non-phylogenetic studies non-phylogenetic models, warning=FALSE, message=FALSE}
tab5=as.data.frame(round(p.adjust(c(0.0001, 0.0001), method = 'fdr'),digit=3),row.names=cbind("Non-phylogenetic","With phylogeny"))
colnames(tab5)<-cbind('P-value')
tab5
```

## Percentage of species with female-biased SSD

```{r Percentage of species with female-biased SSD non-phylogenetic, warning=FALSE, message=FALSE}
Model_cREML_SSbias         = rma.mv(r ~ SSD_SexBias_in_perc_F, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_SSbias)
```

## Test for publication bias

```{r Test for publication bias non-phylogenetic, warning=FALSE, message=FALSE}
Model_cREML_PublBias         = rma.mv(z ~ SE_z, V=rep(((mean(SE_z)*mean(SE_z))*N),length(SE_z)), data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_PublBias)
```

## Publication year
Next we explored the effect of the publication year of each study:
```{r Publication year non-phylogenetic models, warning=FALSE, message=FALSE}
Model_cREML_by_Year = rma.mv(r ~ Year, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Year)
```

# Forest plot
```{r Forest plot setup, warning=FALSE, message=FALSE, results='hide'}
# Sort data by Class
MetaData$Class=as.factor(MetaData$Class)
MetaData$Class=factor(MetaData$Class, levels = c("Animalia","Nematoda","Trematoda","Insecta","Malacostraca","Pisces" ,"Actinopterygii","Amphibia","Mammalia","Reptilia","Aves"))
MetaData_sorted <-MetaData[order(MetaData$r,decreasing = T),]
MetaData_sorted$Class[MetaData_sorted$Class=='Pisces']='Actinopterygii'
MetaData_sorted <-MetaData_sorted[order(MetaData_sorted$Class),]

# Add global effect size to data
forestData=MetaData_sorted[,c(3,5,10,15,18,19)]
forestData[,c(4:6)]=lapply(forestData[,c(4:6)],as.numeric)
forestData$SexSel_Episode=as.factor(forestData$SexSel_Episode)
forestData$SexSel_Episode=factor(forestData$SexSel_Episode, levels = c("pre-copulatory","post-copulatory" ,"both"))
```

## Figure 2
```{r Figure 2, warning=FALSE, message=FALSE, fig.align="left",fig.width = 8.27,fig.height=18, results='hide', fig.fullwidth=TRUE,fig.cap='Figure 2: Forest plot including correlation coefficients (±95% CI), as well as the global effect size (in grey) with and without controlling for phylogeny. Different animal classes highlighted by background colors (see Figure 1 for class names) and sexual selection modes pre- (red), post-copulatory (blue) and both (green) by color of effect size.'}
ggplot(data=forestData, aes(y=1:nrow(forestData), x=r, xmin=lCI, xmax=uCI,color=Class,shape=SexSel_Episode,fill=SexSel_Episode)) +
  geom_vline(xintercept=Model_REML_Null$b[1,1], color='black', linetype='solid', alpha=.9,linewidth=0.75)+
  annotate("rect", xmin = Model_REML_Null$ci.lb[1], xmax = Model_REML_Null$ci.ub[1], ymin = 1, ymax = nrow(forestData),alpha = .25)+
geom_vline(xintercept=0, color='black', linetype='dashed', alpha=.5,linewidth=0.8) +
  geom_errorbarh(height=0,size = ifelse(1:nrow(forestData) == c(1), 3.3, 3.3), alpha=1,colour='white')+
  geom_errorbarh(height=0,size = ifelse(1:nrow(forestData) == c(1), 3.3, 3.3), alpha=1)+
  geom_point(size = ifelse(1:nrow(forestData) == c(1), 2, 2), alpha=1,stroke=1,colour='white')+
  geom_point(size = ifelse(1:nrow(forestData) == c(1), 2, 2), alpha=1,stroke=1,colour='black')+
  scale_y_continuous(breaks=seq(1, nrow(forestData), by=1), labels=forestData$AuthorsAndYear,limits=c(1,length(forestData$AuthorsAndYear)),expand=c(0.015,0.015)) +
  labs(title='', x=expression(paste(italic("r "),'(95% CI)')), y = 'Study') +
  theme_classic()+theme(axis.text.x=element_text(size=12),
                        axis.title=element_text(size=12))+ labs(fill =  c("Sexual selection episode"),shape =  c("Sexual selection mode"))+ 
  scale_colour_manual(values=colpal6, labels=NULL,guide = "none")+
  scale_shape_manual(values=c(21,21,21) ,labels=c("Pre-copulatory","Post-copulatory" ,"Both"))+
  scale_fill_manual(values=c('grey50','white','black'),labels=c("Pre-copulatory","Post-copulatory" ,"Both"))
```