---
title: 'Pre-copulatory sexual selection predicts sexual size dimorphism: a meta-analysis of comparative studies'
author: "Lennart Winkler^1^, Robert P Freckleton^2^, Tamas Szekely^3^, ^4^ & Tim Janicke^1,5^ <br></br>  ^1^Applied Zoology, Technical University Dresden </br></br>^2^Department of Zoology, University of Oxford, South Parks Road, Oxford OX1 3PS, UK<br></br>^3^Milner Centre for Evolution, University of Bath, Bath, UK8</br></br>^4^Department of Evolutionary Zoology and Human Behaviour, University of Debrecen, Debrecen, Hungary</br></br> ^5^Centre d’Écologie Fonctionnelle et Évolutive, UMR 5175, CNRS, Université de Montpellier</br>"
subtitle: 'Additional analyses'
site: workflowr::wflow_site
output:
  workflowr::wflow_html
---

Supplementary material reporting R code for the manuscript 'Pre-copulatory sexual selection predicts sexual size dimorphism: a meta-analysis of comparative studies'.
</br>
Additional analyses excluding studies that did not correct for phylogenetic non-independence (see Supporting Information).
# Load and prepare data
Before we started the analyses, we loaded all necessary packages and data.
```{r Load, message=FALSE, warning=FALSE, results='hide'}
rm(list = ls()) # Clear work environment

# Load R-packages ####
list_of_packages=cbind('ape','matrixcalc','metafor','Matrix','MASS','pwr','psych','multcomp','data.table','ggplot2','RColorBrewer','MCMCglmm','ggdist','cowplot','PupillometryR','dplyr','wesanderson','gridExtra')
lapply(list_of_packages, require, character.only = TRUE)

# Load data set ####
MetaData <- read.csv("./data/Data_SexSelSSD.csv", sep=";", header=TRUE) # Load data set

# Remove studies that did not correct for phylogenetic non-independence
MetaData=MetaData[MetaData$PhyloControlled=='Yes',]

N_Studies <- length(summary(as.factor(MetaData$Study_ID))) # Number of included primary studies

Tree<- read.tree("./data/Pyologeny_SexSelSSD.txt") # Load phylogenetic tree

# Prune phylogenetic tree
MetaData_Class_Data <- unique(MetaData$Class)
Tree_Class<-drop.tip(Tree, Tree$tip.label[-na.omit(match(MetaData_Class_Data, Tree$tip.label))])
forcedC_Moderators <- as.matrix(forceSymmetric(vcv(Tree_Class, corr=TRUE)))

# Order moderator levels
MetaData$SexSel_Episode=as.factor(MetaData$SexSel_Episode)
MetaData$SexSel_Episode=relevel(MetaData$SexSel_Episode,c("post-copulatory"))
MetaData$SexSel_Episode=relevel(MetaData$SexSel_Episode,c("pre-copulatory"))
MetaData$Class=as.factor(MetaData$Class)
MetaData$z=as.numeric(MetaData$z)
```

# Global models
We addressed the question if increasing sexual selection correlated with an increasingly male-biased SSD. For this we ran a global model including an observation-level index and the study identifier as random termson correlation coefficients that were positive if increasing sexual selection correlated with an increasingly male-biased SSD, but negative if increasing sexual selection correlated with an increasingly female-biased SSD. </br></br>
First, we ran a global model including the phylogeny:
```{r Global phylogenetic Model, warning=FALSE, message=FALSE}
Model_REML_Null         = rma.mv(r ~ 1, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_Null)
```

Second, we ran a global model without the phylogeny:
```{r Global non-phylogenetic Model, warning=FALSE, message=FALSE}
Model_cREML_Null         = rma.mv(r ~ 1, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_Null)
```

# Moderator tests for phylogenetic models
Next, we ran a series of models that test the effect of different moderators.</br>
Again we started with models including the phylogeny.

## Sexual selection episode
The first model explores the effect of the sexual selection episode (i.e. pre-copulatory, post-copulatory or both):
```{r Sexual selection Episode, warning=FALSE, message=FALSE}
MetaData$SexSel_Episode=relevel(MetaData$SexSel_Episode,c("pre-copulatory"))
Model_REML_by_SexSelEpisode = rma.mv(r ~ factor(SexSel_Episode), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SexSelEpisode)
```
We then re-leveled the model for post-hoc comparisons:
```{r Sexual selection Episode (re-leveled), warning=FALSE, message=FALSE, results='hide'}
MetaData$SexSel_Episode=relevel(MetaData$SexSel_Episode,c("post-copulatory"))
Model_REML_by_SexSelEpisode2 = rma.mv(r ~ factor(SexSel_Episode), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SexSelEpisode2)

MetaData$SexSel_Episode=relevel(MetaData$SexSel_Episode,c("both"))
Model_REML_by_SexSelEpisode3 = rma.mv(r ~ factor(SexSel_Episode), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SexSelEpisode3)
```
Finally, we computed FDR corrected p-values:
```{r FDR corrected p-values for Sexual selection Episode, warning=FALSE, message=FALSE}
tab1=as.data.frame(round(p.adjust(c(0.0083, 0.3897, .0001), method = 'fdr'),digit=3),row.names=cbind("Pre-copulatory","Post-copulatory","Both"))
colnames(tab1)<-cbind('P-value')
tab1
```
## Sexual selection category
Next we explored the effect of the sexual selection category (i.e. density, mating system, operational sex ratio (OSR), post-mating competition, pre-mating competition, trait-based, other):
```{r Sexual selection category, warning=FALSE, message=FALSE}
MetaData$SexSel_Category=as.factor(MetaData$SexSel_Category)
MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Postmating competition"))
Model_REML_by_SexSelCat = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SexSelCat)
```
We then re-leveled the model for post-hoc comparisons:
```{r Sexual selection category (re-leveled), warning=FALSE, message=FALSE, results='hide'}
MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Trait-based"))
Model_REML_by_SexSelCat2 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SexSelCat2)

MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Density"))
Model_REML_by_SexSelCat3 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SexSelCat3)

MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Premating competition"))
Model_REML_by_SexSelCat4 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SexSelCat4)

MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Mating system"))
Model_REML_by_SexSelCat5 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SexSelCat5)

MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("OSR"))
Model_REML_by_SexSelCat6 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SexSelCat6)

MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Other"))
Model_REML_by_SexSelCat7 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SexSelCat7)
```
Finally, we computed FDR corrected p-values:
```{r FDR corrected p-values for Sexual selection category, warning=FALSE, message=FALSE}
tab2=as.data.frame(round(p.adjust(c(0.1933, 0.9494, 0.1121, 0.0013, 0.0001, .0001, 0.0004), method = 'fdr'),digit=3),row.names=cbind("Postmating competition","Trait-based","Density",'Premating competition',"Mating system","OSR","Other"))
colnames(tab2)<-cbind('P-value')
tab2
```
## Type of SSD measure
Next we explored the effect of the type of SSD measure (i.e. body mass or size):
```{r Type of SSD measure, warning=FALSE, message=FALSE}
MetaData$SSD_Proxy=as.factor(MetaData$SSD_Proxy)
MetaData$SSD_Proxy=relevel(MetaData$SSD_Proxy,c("Body mass"))
Model_REML_by_SSDMeasure = rma.mv(r ~ SSD_Proxy, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SSDMeasure)
```
We then re-leveled the model for post-hoc comparisons:
```{r Type of SSD measure (re-leveled), warning=FALSE, message=FALSE, results='hide'}
MetaData$SSD_Proxy=relevel(MetaData$SSD_Proxy,c("Body size"))
Model_REML_by_SSDMeasure2 = rma.mv(r ~ SSD_Proxy, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_SSDMeasure2)
```
Finally, we computed FDR corrected p-values:
```{r FDR corrected p-values for Type of SSD measure, warning=FALSE, message=FALSE}
tab3=as.data.frame(round(p.adjust(c(.0001, 0.0082), method = 'fdr'),digit=3),row.names=cbind("Body mass","Body size"))
colnames(tab3)<-cbind('P-value')
tab3
```
## SSD measure controlled for body size?
Next we explored the effect if the primary study controlled the SSD for body size (i.e. uncontrolled or controlled):
```{r SSD measure controlled, warning=FALSE, message=FALSE}
MetaData$BodySizeControlled=as.factor(MetaData$BodySizeControlled)
MetaData$BodySizeControlled=relevel(MetaData$BodySizeControlled,c("No"))
Model_REML_by_BodySizeCont = rma.mv(r ~ BodySizeControlled, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_BodySizeCont)
```
We then re-leveled the model for post-hoc comparisons:
```{r SSD measure controlled (re-leveled), warning=FALSE, message=FALSE, results='hide'}
MetaData$BodySizeControlled=relevel(MetaData$BodySizeControlled,c("Yes"))
Model_REML_by_BodySizeCont2 = rma.mv(r ~ BodySizeControlled, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_BodySizeCont2)
```
Finally, we computed FDR corrected p-values:
```{r FDR corrected p-values for SSD measure controlled, warning=FALSE, message=FALSE}
tab4=as.data.frame(round(p.adjust(c(0.0115, 0.1222), method = 'fdr'),digit=3),row.names=cbind("uncontrolled","controlled"))
colnames(tab4)<-cbind('P-value')
tab4
```

## Percentage of species with female-biased SSD
There was variation in the primary studies regarding the typical SSD in the studied taxa (i.e. some studies focused on taxa with more male-biased SSD, while others on taxa with more female-biased SSD). Still, there was no significant relationship between the percentage of species with a female-biased SSD and effect sizes.

```{r Percentage of species with female-biased SSD, warning=FALSE, message=FALSE}
MetaData_SSDbias=MetaData
MetaData_SSDbias=MetaData_SSDbias[!is.na(MetaData_SSDbias$SSD_SexBias_in_perc_F),]
Model_REML_SSbias         = rma.mv(r ~ SSD_SexBias_in_perc_F, V=Var_r, data = MetaData_SSDbias, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_SSbias)
```
## Test for publication bias
To test for publication bias, we transformed r into z scores and ran multilevel mixed-effects models (restricted maximum likelihood) with z as the predictor and its standard error as the response with study ID and an observation level random effect. Models were weight by the mean standard error of z across all studies. While the variance in r depends on the effect size and the sample size, the variance in z is only dependent on the sample size. Hence, if z values correlate with the variance in z, this indicates that small studies were only published, if the effect was large, suggesting publication bias.

```{r Test for publication bias, warning=FALSE, message=FALSE}
Model_REML_PublBias         = rma.mv(z ~ SE_z, V=rep((mean(SE_z)*mean(SE_z))*N,length(SE_z)), data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML",control=list(rel.tol=1e-8))
summary(Model_REML_PublBias)
```
## Publication year
Next we explored the effect of the publication year of each study:
```{r Publication year, warning=FALSE, message=FALSE}
Model_REML_by_Year = rma.mv(r ~ Year, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index, ~ 1 | Class), R = list(Class = forcedC_Moderators), method = "REML")
summary(Model_REML_by_Year)
```

# Moderator tests for non-phylogenetic models
Here we ran all models without the phylogeny.

## Sexual selection episode
The first model explores the effect of the sexual selection episode (i.e. pre-copulatory, post-copulatory or both):
```{r Sexual selection Episode non-phylogenetic models, warning=FALSE, message=FALSE}
MetaData$SexSel_Episode=relevel(MetaData$SexSel_Episode,c("pre-copulatory"))
Model_REML_by_cSexSelEpisode = rma.mv(r ~ factor(SexSel_Episode), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cSexSelEpisode)
```
We then re-leveled the model for post-hoc comparisons:
```{r Sexual selection Episode (re-leveled) non-phylogenetic models, warning=FALSE, message=FALSE, results='hide'}
MetaData$SexSel_Episode=relevel(MetaData$SexSel_Episode,c("post-copulatory"))
Model_REML_by_cSexSelEpisode2 = rma.mv(r ~ factor(SexSel_Episode), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cSexSelEpisode2)

MetaData$SexSel_Episode=relevel(MetaData$SexSel_Episode,c("both"))
Model_REML_by_cSexSelEpisode3 = rma.mv(r ~ factor(SexSel_Episode), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index),  method = "REML")
summary(Model_REML_by_cSexSelEpisode3)
```
Finally, we computed FDR corrected p-values:
```{r FDR corrected p-values for Sexual selection mode non-phylogenetic models, warning=FALSE, message=FALSE}
tab1=as.data.frame(round(p.adjust(c(0.0001, 0.3058, .0001), method = 'fdr'),digit=3),row.names=cbind("Pre-copulatory","Post-copulatory","Both"))
colnames(tab1)<-cbind('P-value')
tab1
```

## Sexual selection category
Next we explored the effect of the sexual selection category (i.e. density, mating system, operational sex ratio (OSR), post-mating competition, pre-mating competition, trait-based, other):
```{r Sexual selection category non-phylogenetic models, warning=FALSE, message=FALSE}
MetaData$SexSel_Category=as.factor(MetaData$SexSel_Category)
MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Postmating competition"))
Model_REML_by_cSexSelCat = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cSexSelCat)
```
We then re-leveled the model for post-hoc comparisons:
```{r Sexual selection category (re-leveled) non-phylogenetic models, warning=FALSE, message=FALSE, results='hide'}
MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Trait-based"))
Model_REML_by_cSexSelCat2 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cSexSelCat2)

MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Density"))
Model_REML_by_cSexSelCat3 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cSexSelCat3)

MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Premating competition"))
Model_REML_by_cSexSelCat4 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cSexSelCat4)

MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Mating system"))
Model_REML_by_cSexSelCat5 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cSexSelCat5)

MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("OSR"))
Model_REML_by_cSexSelCat6 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cSexSelCat6)

MetaData$SexSel_Category=relevel(MetaData$SexSel_Category,c("Other"))
Model_REML_by_cSexSelCat7 = rma.mv(r ~ factor(SexSel_Category), V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cSexSelCat7)
```
Finally, we computed FDR corrected p-values:
```{r FDR corrected p-values for Sexual selection category non-phylogenetic models, warning=FALSE, message=FALSE}
tab2=as.data.frame(round(p.adjust(c(0.2833, 0.9816, 0.0176, .0001, .0001, .0001, .0001), method = 'fdr'),digit=3),row.names=cbind("Postmating competition","Trait-based","Density",'Premating competition',"Mating system","OSR","Other"))
colnames(tab2)<-cbind('P-value')
tab2
```

## Phylogenetic classes
Next we explored the effect of the phylogenetic classes:
```{r Phylogenetic classes, warning=FALSE, message=FALSE}
MetaData$Class=relevel(MetaData$Class,c("Actinopterygii"))
Model_cREML_by_Class5 = rma.mv(r ~ Class, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Class5)

MetaData$Class=relevel(MetaData$Class,c("Amphibia"))
Model_cREML_by_Class4 = rma.mv(r ~ Class, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Class4)

MetaData$Class=relevel(MetaData$Class,c("Animalia"))
Model_cREML_by_Class11 = rma.mv(r ~ Class, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Class11)

MetaData$Class=relevel(MetaData$Class,c("Aves"))
Model_cREML_by_Class = rma.mv(r ~ Class, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Class)

MetaData$Class=relevel(MetaData$Class,c("Insecta"))
Model_cREML_by_Class8 = rma.mv(r ~ Class, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Class8)

MetaData$Class=relevel(MetaData$Class,c("Mammalia"))
Model_cREML_by_Class3 = rma.mv(r ~ Class, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Class3)

MetaData$Class=relevel(MetaData$Class,c("Nematoda"))
Model_cREML_by_Class10 = rma.mv(r ~ Class, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Class10)

MetaData$Class=relevel(MetaData$Class,c("Pisces"))
Model_cREML_by_Class6 = rma.mv(r ~ Class, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Class6)

MetaData$Class=relevel(MetaData$Class,c("Reptilia"))
Model_cREML_by_Class2 = rma.mv(r ~ Class, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Class2)

MetaData$Class=relevel(MetaData$Class,c("Trematoda"))
Model_cREML_by_Class9 = rma.mv(r ~ Class, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Class9)
```
Finally, we computed FDR corrected p-values:
```{r FDR corrected p-values for Phylogenetic classes, warning=FALSE, message=FALSE}
tab2=as.data.frame(round(p.adjust(c(0.0042, 0.8853, .0001, 0.4463, 0.0537, 0.3192, 0.0587, 0.9535, 0.0503, 0.2432), method = 'fdr'),digit=3),row.names=cbind( "Animalia","Nematoda","Trematoda","Insecta","Pisces" ,"Actinopterygii","Amphibia","Mammalia","Reptilia","Aves"))
colnames(tab2)<-cbind('P-value')
tab2
```

## Type of SSD measure
Next we explored the effect of the type of SSD measure (i.e. body mass or size):
```{r Type of SSD measure non-phylogenetic models, warning=FALSE, message=FALSE}
MetaData$SSD_Proxy=as.factor(MetaData$SSD_Proxy)
MetaData$SSD_Proxy=relevel(MetaData$SSD_Proxy,c("Body mass"))
Model_REML_by_cSSDMeasure = rma.mv(r ~ SSD_Proxy, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cSSDMeasure)
```
We then re-leveled the model for post-hoc comparisons:
```{r Type of SSD measure (re-leveled) non-phylogenetic models, warning=FALSE, message=FALSE, results='hide'}
MetaData$SSD_Proxy=relevel(MetaData$SSD_Proxy,c("Body size"))
Model_REML_by_cSSDMeasure2 = rma.mv(r ~ SSD_Proxy, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cSSDMeasure2)
```
Finally, we computed FDR corrected p-values:
```{r FDR corrected p-values for Type of SSD measure non-phylogenetic models, warning=FALSE, message=FALSE}
tab3=as.data.frame(round(p.adjust(c(.0001, 0.0006), method = 'fdr'),digit=3),row.names=cbind("Body mass","Body size"))
colnames(tab3)<-cbind('P-value')
tab3
```

## SSD measure controlled for body size?
Next we explored the effect if the primary study controlled the SSD for body size (i.e. uncontrolled or controlled):
```{r SSD measure controlled non-phylogenetic models, warning=FALSE, message=FALSE}
MetaData$BodySizeControlled=as.factor(MetaData$BodySizeControlled)
MetaData$BodySizeControlled=relevel(MetaData$BodySizeControlled,c("No"))
Model_REML_by_cBodySizeCont = rma.mv(r ~ BodySizeControlled, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cBodySizeCont)
```
We then re-leveled the model for post-hoc comparisons:
```{r SSD measure controlled (re-leveled) non-phylogenetic models, warning=FALSE, message=FALSE, results='hide'}
MetaData$BodySizeControlled=relevel(MetaData$BodySizeControlled,c("Yes"))
Model_REML_by_cBodySizeCont2 = rma.mv(r ~ BodySizeControlled, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_REML_by_cBodySizeCont2)
```
Finally, we computed FDR corrected p-values:
```{r FDR corrected p-values for SSD measure controlled non-phylogenetic models, warning=FALSE, message=FALSE}
tab4=as.data.frame(round(p.adjust(c(.0001, 0.0712), method = 'fdr'),digit=3),row.names=cbind("uncontrolled","controlled"))
colnames(tab4)<-cbind('P-value')
tab4
```

## Percentage of species with female-biased SSD

```{r Percentage of species with female-biased SSD non-phylogenetic, warning=FALSE, message=FALSE}
Model_cREML_SSbias         = rma.mv(r ~ SSD_SexBias_in_perc_F, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_SSbias)
```

## Test for publication bias

```{r Test for publication bias non-phylogenetic, warning=FALSE, message=FALSE}
Model_cREML_PublBias         = rma.mv(z ~ SE_z, V=rep(((mean(SE_z)*mean(SE_z))*N),length(SE_z)), data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_PublBias)
```

## Publication year
Next we explored the effect of the publication year of each study:
```{r Publication year non-phylogenetic models, warning=FALSE, message=FALSE}
Model_cREML_by_Year = rma.mv(r ~ Year, V=Var_r, data = MetaData, random = c(~ 1 | Study_ID,~ 1 | Index), method = "REML")
summary(Model_cREML_by_Year)
```